### 2016-03-28 chapters/conclusion.tex
todos are now in the pdf

We also introduce a questionnaire to support the configuration of a product from the given product line. A questionnaire needs to be designed carefully by the developers or experts on the domain of the product line. It allows a mapping between answers to simple questions and actual features of the product line. With this method, a user doesn't have to undergo the process of configuration in the sense of (un-)selecting a specific set of features. Instead he only has to answer questions according to his use case to do the configuration of his specific product. As the tool uses the underlying FeatureIDE, it also makes use of it's functions, e.g. validity checks. This additionally supports the usability and correctness of the whole process.

>>>>

We also introduce a questionnaire to support the configuration of a product from the given product line. A questionnaire needs to be designed carefully by the developers or experts on the domain of the product line. It allows a mapping between answers to simple questions and actual features of the product line. With this method, a user doesn't have to undergo the process of configuration in the sense of (un-)selecting a specific set of features. Instead, he only has to answer questions according to his use case to do the configuration of his specific product. As the tool uses the underlying FeatureIDE, it also makes use of its functions, e.g. validity checks. This additionally supports the usability and correctness of the whole process.
